Merging Datasets Through Deep learning

### 2018-08-30 paper2018/relatedWork.tex
edits

\section{Related Work}
Extensions in data management systems for handling joins across different spellings for instance, typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).

>>>>

\section{Related Work}
Extensions in data management systems for handling joins across different spellings for instance, typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than to \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).
